The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2012-06-11 smurf_paper.tex
finish draft + re-made extended plots. Also minor updates throughout paper

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2006} is a new instrument for the 15-m James
Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
simultaneously images the sky in two broad bands centered over 450 and
850\,\micron. The focal planes at each wavelength are populated with 4
rectangular subarrays, consisting of $40 \times 32$ bolometers each,
and subtend a nearly contiguous $4' \times 4'$ footprint on the sky.
Ultimately, the instrument will also be equipped with a Fourier
transform spectrometer \citep[FTS-2,][]{gom2010}, and a polarimeter
\cite[POL-2,][]{bastien2005}. This paper describes the Submillimetre
User Reduction Facility, SMURF, a software package for reducing the
imaging data. The reduction of FTS-2 and POL-2 data will be described
at a later date once these additional instruments have been
commissioned. The details of the instrument design, performance, and
its calibration are given in two companion papers: \citet{holland2012}
and \citet{dempsey2012}.

@@

\begin{table}
  \caption{Summary of the model components that can be fit to
    \scuba\ time-series data with SMURF. Only the first group of
    models (in the order indicated) are typically fit to the data
    (\model{COM}--\model{NOI}) in the indicated order. The remaining
    models (\model{DKS}--\model{PLN}) have only been included for
    completeness}
  \vspace{0.2cm}
  \centering
  \begin{tabular}{c|l}
    \hline
    Model & Description \\
    \hline
    \model{COM} & remove common-mode signal \\
    \model{GAI} & common-mode scaled to each bolometer \\
    \model{EXT} & extinction correction \\
    \model{FLT} & Fourier transform filter \\
    \model{AST} & map estimate of astronomical signal \\
    \model{NOI} & noise estimation \\
    \hline
    \model{DKS} & dark squid cleaning along columns \\
    \model{SMO} & time-domain smoothing filter \\
    \model{PLN} & 2-dimensional time-varying plane removal \\
    \hline
    \end{tabular}
  \label{tab:components}
\end{table}

@@

\subsubsection{\model{DKS}: dark squid cleaning along columns}
\label{sec:dks}

@@

\subsubsection{\model{TMP}: remove a scaled template}

@@

\subsubsection{\model{SMO}: time-domain smoothing filter}
\label{sec:smo}

@@

\subsubsection{\model{PLN}: 2d time-varying sky noise plane removal}
\label{sec:pln}

@@

@@

\subsubsection{Whitening filter}

EC

@@

In this section three different types of data are reduced. In each
case, the baseline reduction using defaults as described in
Section~\ref{sec:algorithm} are used first. Then, modifications are
described to improve each reduction.

\subsection{Known point source}
\label{sec:point}

@@

\subsection{Deep blind survey}
\label{sec:cosmo}

@@

\subsection{Bright extended emission}

In this final example, we analyze a map of M17 which contains bright,
extended emission, in contrast with the earlier two examples. A
promise of \scuba\ is to recover larger angular scales than what was
possible with earlier-generation ground-based submillimetre
cameras. The two main factors contributing to this expectation are:
(i) a larger array footprint on the sky which should make the
subtraction of common sky-emission signals more effective; and (ii)
fast detectors (with a correspondingly fast sample rate) to enable
higher slew-rates (up to 600\,arcsec\,s$^{-1}$) to capture as much
large-scale structure as possible above the detector $1/f$ knees. We
produce maps of observation 11 on 20110531 using the 850\,\micron\
array. It is a rotating PONG convering a diameter of 0.375\,deg, with
a scan speed of 300\,arcsec\,s$^{-1}$, and a transverse spacing of
180\,arcsec, taking 37.5\,min to complete.

The default reduction of these data is shown in the top panels of
Fig.~\ref{fig:m17}, after iterations 2 (the first map estimated after
the noise weights have been measured) and 30 iterations (when the map
has converged). The first panel also depicts the array footprint, and
the angular scale corresponding the high-pass filter edge. Much like
the reduction of a point source without any prior constraints
(Fig.~\ref{fig:pointmaps}c), degeneracies on scales larger than the
array footprint and filter produce ripples in the map.

@@

\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{m17_jk.pdf}
\caption{Maps of M17 used to characterize the noise properties and
transfer function of SMURF. For each column, a different high-pass
filter edge scale was adopted (indicated in the top panels). First
(top) row: Average of two halves of the data analyzed independently,
using the default configuration. The data have had added to them
synthetic signal within a 600\,arcsec diameter circle (S.E. of M17)
created as a realization of noise from a $P(k) \propto k^{-3}$ angular
power spectrum multiplied by the PSF, subtracting the minimum to make
it positive, scaling it to a similar signal range as M17 itself, and
rolling-off the edges smoothly using half a period of a radial
(1+cosine)/2 function across 100\,arcsec beyond the edge of the
600\,arcsec region. Second row: jackknife maps produced from the
differences of the maps of each half of the data that went into the
first row. Third row: average of the two halves of the data using the
bright extended reduction. The blue and red contours indicated the
zero-masked regions in each case (note for the 300\,arcsec case that
the region about M17 matches fairly closely the mask in
Fig.~\ref{fig:m17}d). Clearly as the filter scale is increased, due to
the high SNR of the data, larger emissions regions are (correctly)
detected and reproduced in the map. Fourth (bottom) row: Jackknife
maps for the bright extended reductions.}
\label{fig:m17_jk}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_m17_default.pdf}
\includegraphics[width=0.49\linewidth]{cor_pspec_m17_default.pdf}
\caption{Angular power spectral densities (PSDs) for the region of the
M17 map in Fig.~\ref{fig:m17_jk} containing synthetic data, using the
default configuration. left: raw PSDs for the input (noiseless)
simulated data (thick black line), the signal (average of each half)
PSDs (thin solid lines), and noise PSDs estimated from the jackknives
(dashed lines). Vertical dotted lines indicate the high-pass filter
scales. The red, green, and blue colours indicate data filtered at
150, 300, and 600\,arcsec scales. right: corrected PSDs. Since the
input PSD is known, it is possible to measure the transfer function of
the map-maker as the ratio between the output map signal and input
PSDs (thick solid lines). The remaining lines are as in the left
panel, but now corrected by the transfer function. This plot shows
that while increasing the filter scale improves the SNR at large
scales ($\gsim100$\,arcsec), it also reduces the SNR at smaller scales
($\lsim100$\,arcsec).}
\label{fig:m17_def_ps}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_m17_bright_extended.pdf}
\includegraphics[width=0.49\linewidth]{cor_pspec_m17_bright_extended.pdf}
\caption{Lines have same meaning as in Fig.~\ref{fig:m17_def_ps},
except now using the bright extended configuration. This configuration
has resulted in an improved transfer function and SNR at large angular
scales. Also note that increasing the filter scale does not have as
large of an impact on the small-scale noise as in the default
configuration.}
\label{fig:m17_bc_ps}
\end{figure*}

While the reduction in the bottom panels of Fig.~\ref{fig:m17} is
clearly superior in at least a cosmetic sense to those in the top
panels, it is important to quantify both the noise properties of the
maps and their response to real structures (the transfer function). We
would also like to know these are affected by our choice of filter
scale.  Similar to the previous section, we will use a jackknife test
to estimate the noise, and then inject known sources into the data to
observe how they are attenuated.

Maps are produced using the first and second continuous halves of the
data in Fig.~\ref{fig:m17_jk}. This is not an ideal situation since
the noise properties may evolve with time (e.g., due to changing sky
conditions) leading to a biased estimate of the parent noise
distribution from the jackknife. Also, since the zero-masking depends
on the SNR of the map, it will be restricted to regions approximately
$\sqrt{2}$ shallower in these maps than for the full data
set. Finally, the cross-linking (positional angles sampled) is
similar, though not identical in the two halves. Ideally one would
have many full maps as in the case of the Lockman Hole data in the
previous section, from which alternating maps could be combined.

%A second map of M17 using the same observing mode was made shortly
%after the first, observation 13 on 20110511. We produce jackknife maps
%from the differences between the two ... angular power spectrum of the
%noise (should be worse at large-scale for the default map).

In addition to dividing the data into two halves, we also inject
simulated clouds into a relative empty portion of the map. It is
created by drawing a realization of noise within an 800\,arcsec
on-a-side box, from an angular power spectrum $P(k) \propto k^{-3}$
which is appropriate for Galactic cirrus clouds
\citep[e.g.][]{gautier1992}. It is then filtered again with a
14.5\,arcsec Gaussian to model the effect of the SCUBA-2 optical
response. The RMS of these fluctuations are then normalized to 0.002
pW so that they are comparable to the dynamic range of M17 itself. The
minimum is subtracted so that the signal is positive. Finally, half a
period of a (1+cosine)/2 function is used to roll-off the signal to
zero between radii of 300 and 400 arcsec.

The first row of Fig.~\ref{fig:m17_jk} shows the total signal image
averaging the maps made of each independent half of the data, for the
default configuration (inverse-variance weighting has been used). The
columns show reductions using 150, 300, and 600\,arcsec filter edges
in the reductions. The synthetic data are clearly seen as the circular
region S.E. of M17. As the filter scale is increased, the size of the
ripples increases accordingly. While larger structures do seem to
appear, negative bowls are a major problem without any other map
constraints.The second row of Fig.~\ref{fig:m17_jk} shows the
jackknife maps. The astronomical emission is almost perfectly removed,
except for a slight impression of M17 near the centre of the map that
is probably due to some combination of detector gain and pointing
drifts.

One fairly arbitrary parameter in our data reduction is the choice of
angular scale for the \model{FLT} filter. The current default of
300\,arcsec\ was chosen ``by-eye'' as a compromise that would provides
aesthetically reasonable results for a range of observing
modes. However, there is a simple tradeoff that warrants
experimentation for specific fields. By choosing a larger scale (lower
frequency in the bolometers signals) for the filter, potentially more
structure will be faithfully re-produced in the map (up to the scale
of the array footprint, at which point the common-mode removal will
dominate). However, lower the filter edge can potentially let through
more independent low-frequency noise. We have therefore re-run the
previous tests using two other scales for the filters, and show the
resulting maps and angular SNR spectra in Figs ... .

Note that alternatives to the zero-masking approach do exist for other
iterative map-makers. For example, \citet{kovacs2008} restricts the
solution to a small number of iterations to avoid divergence on
large-scales. For BOLOCAM data of the Galactic Plane,
\citet{aguirre2010} used a Maximum-Entropy filtering step to suppress
large-scales. The zero-masking implemented in SMURF is similar in
principle to the \citet{aguirre2010} method, while being slightly
conceptually simpler. However, since both methods are non-linear,
detailed simulations would be required to determine their
SNR-dependent angular transfer functions.

\textit{Or now an externally supplied mask.}

@@

\scuba\ is being re-commissioned. Maybe we will have some initial data
on fridge performance? If both it, and sky noise are relatively
well-behaved, might be able to restrict filtering to lower frequencies
and get larger-scale structures.

Larger array footprint also helps.

Talk about potential of Pascale et al. method to get closer to
max-likelihood map solution (handle maps at constant scan angles with
weights in Fourier space separately).

>>>>

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2006} is a new instrument for the 15-m James
Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
simultaneously images the sky in two broad bands centered over 450 and
850\,\micron. The focal planes at each wavelength are populated with 4
rectangular subarrays, consisting of $40 \times 32$ bolometers each,
and subtend a nearly contiguous $7' \times 7'$ footprint on the sky.
Ultimately, the instrument will also be equipped with a Fourier
transform spectrometer \citep[FTS-2,][]{gom2010}, and a polarimeter
\cite[POL-2,][]{bastien2005}. This paper describes the Submillimetre
User Reduction Facility, SMURF, a software package for reducing the
imaging data. The reduction of FTS-2 and POL-2 data will be described
at a later date once these additional instruments have been
commissioned. The details of the instrument design, performance, and
its calibration are given in two companion papers: \citet{holland2012}
and \citet{dempsey2012}.

@@

\begin{table}
  \caption{Summary of the model components that can be fit to
    \scuba\ time-series data with SMURF. Only the first group of
    models (in the order indicated) are typically fit to the data
    (\model{COM}--\model{NOI}) in the indicated order. The remaining
    models (\model{DKS}--\model{PLN}) have only been included for
    completeness}
  \vspace{0.2cm}
  \centering
  \begin{tabular}{c|l}
    \hline
    Model & Description \\
    \hline
    \model{COM} & remove common-mode signal \\
    \model{GAI} & common-mode scaled to each bolometer \\
    \model{EXT} & extinction correction \\
    \model{FLT} & Fourier transform filter \\
    \model{AST} & map estimate of astronomical signal \\
    \model{NOI} & noise estimation \\
    \hline
    \model{DKS} & dark squid cleaning along columns \\
    \model{PLN} & 2-dimensional time-varying plane removal \\
    \model{SMO} & time-domain smoothing filter \\
    \model{TMP} & pointing as baseline template \\
    \hline
    \end{tabular}
  \label{tab:components}
\end{table}

@@

\subsubsection{Other experimental models}

We don't use them, but we should mention them since a reviewer might
ask us if we tried them: \model{DKS}, \model{TMP}, \model{SMO},
\model{PLN}.

@@

@@

@@

@@

Another major source of divergence is correlation between \model{COM}
and \model{FLT}. Since \model{FLT} usually consists of a high-pass
filter following the application of \model{COM}, \model{COM} is
completely free to grow any large-scale structure at frequencies below
the chosen filter edge. While such structure does not appear in the
map (as it is removed by \model{FLT}), we found that the solution
could be made to converge significantly faster by ``re-mixing''
\model{COM} and \model{FLT} at the start of each iteration. In
practice, at the start of each iteration, the previous iterations of
each model are both added back into the residual immediately prior to
re-calculating \model{COM}. In this way, truly common-mode signals,
even at low-frequencies, do not leak into \model{FLT}.

@@

\subsubsection{Bolometer Filtering}

Despite the ability of the map-maker to iterative remove many noise
components, under some circumstances it may be desirable to filter the
data \emph{once} during the pre-processing step. Three main filtering
options are available:

\item The most commonly-used pre-processing filter is polynomial
subtraction. A polynomial of the requested order is fit and removed
from each bolometer time-series. At a bare minimum, the mean is
removed from all of the bolometers (order 0) in all reductions
described in this paper.

\item All of the filters available as part of the iterative Fourier
Transform Filter (Section~\ref{sec:flt}) can also be applied once
during pre-processing.

\item As a complete alternative to the iterative map-making procedure,
cleaning by principal component analysis (PCA) is available as an
experimental pre-processing option. As described in
Section~\ref{sec:pca}, a new set of basic vectors for the bolometer
data are found which diagonalize their covariance matrix. The
brightest components can then be subtracted from the data. A single
parameter specifies the threshold on the amplitude of the eigenvalues
to be removed, as a number of standard deviations away from the mean
value. Subarrays are cleaned independently once for the full length of
each continuousy chunk of data. Given the computational expense of
this method, and initial tests which showed little improvement over
simple high-pass filtering, this method has not yet been explored in
detail with SCUBA-2 data.

@@

In this section three different common types of data are reduced: a
bright point source, Uranus (Section~\ref{sec:point}); a bind survey
of high-redshift galaxies in the Lockman Hole
(Section~\ref{sec:cosmo}); and a map of a bright extended star-forming
region in our Galaxy, M17 (Section~\ref{sec:extended}). In each case,
variations on the default algorithm from Section~\ref{sec:algorithm}
are described.

%-------------------------------------------------
\subsection{Known point source}
\label{sec:point}
%-------------------------------------------------

@@

%-------------------------------------------------
\subsection{Deep blind survey}
\label{sec:cosmo}
%-------------------------------------------------

@@

%-------------------------------------------------
\subsection{Bright extended emission}
\label{sec:extended}
%-------------------------------------------------

In this final example, we analyze a map of M17 which contains bright,
extended emission, in contrast with the earlier two examples. A
promise of \scuba\ is to recover larger angular scales than what was
possible with earlier-generation ground-based submillimetre
cameras. The two main factors contributing to this expectation are:
(i) a larger array footprint on the sky which should make the
subtraction of common sky-emission signals more effective; and (ii)
fast detectors (with a correspondingly fast sample rate) to enable
higher slew-rates (up to 600\,arcsec\,s$^{-1}$) to capture as much
large-scale structure as possible above the detector $1/f$ knees. We
produce maps of observation 11 on 20110531 using the 850\,\micron\
array. It is a rotating PONG covering a diameter of 0.375\,deg, with a
scan speed of 300\,arcsec\,s$^{-1}$, and a transverse spacing of
180\,arcsec, taking 37.5\,min to complete.

The default reduction of these data is shown in the top panels of
Fig.~\ref{fig:m17}, after iterations 2 (the first map estimated after
the noise weights have been measured) and 17 iterations (when the map
has converged). The first panel also depicts the array footprint, and
the angular scale corresponding to the high-pass filter edge. Much
like the reduction of a point source without any prior constraints
(Fig.~\ref{fig:pointmaps}c), degeneracies on scales larger than the
array footprint and filter produce ripples in the map.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{m17_jk.pdf}
\caption{Maps of M17 used to characterize the noise properties and
transfer function of SMURF (same intensity scale as
Fig.~\ref{fig:m17}). For each column, a different high-pass filter
edge scale was adopted (indicated in the top panels). First (top) row:
Average of two halves of the data analyzed independently, using the
default configuration. The data have had added to them synthetic
signal within a 600\,arcsec diameter circle (S.E. of M17) created as a
realization of noise from a $P(k) \propto k^{-3}$ angular power
spectrum multiplied by the PSF, subtracting the minimum to make it
positive, scaling it to a similar signal range as M17 itself, and
rolling-off the edges smoothly using half a period of a radial
(1+cosine)/2 function across 100\,arcsec beyond the edge of the
600\,arcsec region. Second row: jackknife maps produced from the
differences of the maps of each half of the data that went into the
first row. Third row: average of the two halves of the data using the
bright extended reduction. The blue and red contours indicated the
zero-masked regions in each case (note for the 300\,arcsec case that
the region about M17 matches fairly closely the mask in
Fig.~\ref{fig:m17}d). Clearly as the filter scale is increased, due to
the high SNR of the data, larger emissions regions are (correctly)
detected and reproduced in the map. Fourth (bottom) row: Jackknife
maps for the bright extended reductions.}
\label{fig:m17_jk}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_m17_default.pdf}
\includegraphics[width=0.49\linewidth]{cor_pspec_m17_default.pdf}
\caption{Angular power spectral densities (PSDs) for the region of the
M17 map in Fig.~\ref{fig:m17_jk} containing synthetic data, using the
default configuration. left: raw PSDs for the input (noiseless)
simulated data (thick black line), the signal (average of each half)
PSDs (thin solid lines), and noise PSDs estimated from the jackknives
(dashed lines). Vertical dotted lines indicate the high-pass filter
scales: 150\,arcsec (red); 300\,arcsec (orange); 600\,arcsec (green);
and 900\,arcsec (blue). Since the input PSD is known, it is possible
to measure the transfer function of the map-maker as the ratio between
the output map signal PSDs and the input PSD (from the left panel),
giving the thin coloured lines (linear vertical axis shown on right of
plot). The remaining lines are as in the left panel, but now corrected
by the transfer function. This plot shows that increasing the filter
scale improves the SNR at intermediates scales
($\sim$200--600\,arcsec), although the SNR worsens at smaller scales
($\lsim$200\,arcsec).}
\label{fig:m17_def_ps}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_m17_bright_extended.pdf}
\includegraphics[width=0.49\linewidth]{cor_pspec_m17_bright_extended.pdf}
\caption{Lines have same meaning as in Fig.~\ref{fig:m17_def_ps},
except now using the bright extended configuration. This configuration
has resulted in an improved transfer function and SNR at large angular
scales. Also note that increasing the filter scale does not have as
large of an impact on the small-scale noise as in the default
configuration, although it is still noticeably larger up to scales of
about $\sim$60\,arcsec.}
\label{fig:m17_be_ps}
\end{figure*}

While the reduction in the bottom panels of Fig.~\ref{fig:m17} is
clearly superior in at least a cosmetic sense to those in the top
panels, it is important to quantify both the noise properties of the
maps and their response to real structures (the transfer function). We
would also like to know how each are affected by our choice of filter
scale.  Similar to the previous section, we will use a jackknife test
to estimate the noise, as well as injecting known sources into the
data to observe how they are attenuated.

Maps are produced using the first and second continuous halves of the
data in Fig.~\ref{fig:m17_jk}. This is not an ideal situation since
the noise properties may evolve with time (e.g., due to changing sky
conditions) leading to a biased estimate of the parent noise
distribution in the complete map from the jackknife. Also, since the
zero-masking depends on the SNR of the map, it will be restricted to
regions approximately $\sqrt{2}$ shallower in these maps than for the
full data set. Finally, the cross-linking (positional angles sampled)
is similar, though not identical in the two halves. Ideally one would
have many full maps as in the case of the Lockman Hole data in the
previous section, from which alternating maps could be combined.

Since our goal in this section is to measure the response of the
map-maker to extended structures, we inject a simulated signal with
power at a range of scales to a relatively empty region of the map.
It is created by drawing a realization of noise within an 800\,arcsec
on-a-side box, with an angular power spectrum $P(k) \propto k^{-3}$
which is appropriate for Galactic cirrus clouds
\citep[e.g.][]{gautier1992}. It is then filtered again with a
14.5\,arcsec Gaussian to model the effect of the SCUBA-2 optical
response. The RMS of these fluctuations are then normalized to 0.002
pW so that they are comparable to the dynamic range of M17 itself. The
minimum is subtracted so that the signal is positive. Finally, half a
period of a (1+cosine)/2 function is used to roll-off the signal to
zero between radii of 300 and 400 arcsec.

The first row of Fig.~\ref{fig:m17_jk} shows the total signal image
averaging the maps made of each independent half of the data, for the
default configuration (inverse-variance weighting has been used). The
columns show reductions using 150, 300, 600, and 900\,arcsec filter
edges in the reductions. For reference, the largest scale that is
completely inscribed by the array footprint is about 400\,arcsec, and
the diagonal of the array is about 600\,arcsec (meaning that scales
beyond 600\,arcsec are completely unconstrained when common-mode
rejection is used).  The synthetic data are clearly seen as the
circular region S.E. of M17. As the filter scale is increased, the
size of the ripples increases accordingly. While larger structures do
seem to appear, negative bowls are a major problem without any other
map constraints.The second row of Fig.~\ref{fig:m17_jk} shows the
jackknife maps. The astronomical emission is almost perfectly removed,
except for a slight impression of M17 near the centre of the map that
is probably due to some combination of detector gain and pointing
drifts. Otherwise the jackknife appears to be a plausible realization
of noise from the same parent distribution as for the averaged maps.

The third and fourth rows in Fig.~\ref{fig:m17_jk} repeat this
exercise using the bright extended configuration, in which the SNR
threshold of 5 is again used to constrain the map. As the filter scale
is increased, more of the extended structure in M17 is reproduced in
the map, as evidenced by the blue and red contours (masks generated
from the first and second halves of the data, respectively). The
masking does a generally good job of suppressing the largest-scale
ripples that are produced by the default reduction. However, the noise
away from regions of bright emission does increase noticeably (mottled
appearance). With filter scales $\gsim600$\,arcsec, virtually the
entire region of synthetic emission is correctly identified by the SNR
mask and allowed to vary freely in the solution.

Next, we analyze the angular power spectra densities (PSDs) of the
maps to understand the signal and noise properties of the map-maker in
the region of synthetic sources, as a function of filter scale. The
left panel of Fig.~\ref{fig:m17_def_ps} shows the raw PSDs for the
input synthetic signal (thick black line), the output map signals
(thin solid lines), and the jackknife maps (dashed lines). Colours
encode the filter scales used: 150\,arcsec (red); 300\,arcsec
(orange); 600\,arcsec (green); and 900\,arcsec (blue). Note that, in
the exception of the synthetic data, we only plot the PSDs down two
the second-lowest spatial frequency bin of
$1.875\times10^{-3}$\,arcsec$^{-1}$, or 533\,arcsec, due to the fact
that the smallest is very poorly sampled, and therefore noisy. As the
filter edge is increased, more power is measured in the map PSDs at
larger scales. However, much of this power is clearly produced by
noise which appears in the jackknife PSDs. We estimate the map-maker
transfer function as the ratio between the portion of the signal PSDs
\emph{not} produced by noise, to the input PSD, or
%
\begin{equation}
G(k) = \frac{P_\mathrm{M}(k) - P_\mathrm{JK}(k)}{P_\mathrm{S}(k)},
\end{equation}
%
where $k$ is the spatial frequency, and the subscripts ``M'', ``JK'',
and ``S'' refer to the signal map, jackknife map, and synthetic map,
respectively.

The transfer functions $G(k)$ are plotted as thin solid lines in the
right panel of Fig.~\ref{fig:m17_def_ps}. This formula produced
extremely noisy values at large frequencies (small scales), and was
set to a value of 1 above 0.015\,arcsec$^{-1}$, as well as any point
in the curve where $P_\mathrm{M}(k)$ exceeded $P_\mathrm{S}(k)$
(i.e. $G(K)$ is assumed to be $\le$1). As expected, the larger the
scale of the filter, the lower the spatial frequency at which the map
transfer function falls. We then correct the map and jackknife PSDs by
dividing by $G(k)$ to produce the thick solid, and dashed lines in the
right panel of Fig.~\ref{fig:m17_def_ps}. This shows us that, even
though the raw noise in the left panel is lower at small scales when a
smaller-scale filter is used (e.g. the red dashed line), once we
correct for the transfer function, we actually win in a SNR sense at
large scales using the larger-scale filter as you would expect.

These tests are then repeated using the bright extended reduction in
Fig.~\ref{fig:m17_be_ps}. The most obvious improvement with this
reduction over the default reduction is that the transfer functions
fall more slowly at large angular scales, accompanied by a slower
increase in noise; in other words, there is greatly improved SNR at
large angular scales (an obvious conclusion given the appearence of
the maps in Fig.~\ref{fig:m17_jk}). In fact, using the 900\,arcsec
filter edge, the map response is still above 80\% right out to the
largest scale accurately measured in the PSDs, 533\,arcsec, which is
about the largest scale that should be recoverable given the size of
the array footprint and the fact that we use common-mode rejection.
Another interesting feature of these reductions is that the increase
in small-scale noise as the filter edge is increased is not as drastic
as in the default reduction, and the SNR improves at scales
$\gsim$60\,arcsec.

One case in which the SNR is \emph{worse} using the bright extended
reduction is using a 150\,arcsec filter. In this case the noise is
considerably larger in the bright extended reduction as evidenced by
the ``kink'' near 150\,arcsec. Referring to the mask contours in the
left panel of the third row, it is clear that the map-maker has failed
to identify much of the bright, extended emission in the region of the
synthetic source. Each area that is not within the contours is
constrained to zero throughout the solution, therefore suppressing
power (and lowering the transfer function), and subsequently reducing
the SNR of the final result. This measurement serves as a warning: the
map-maker response is non-linear when using SNR masking. Harsh
filtering can provide misleading results as in this example. Maps of
\emph{faint} extended emission will also suffer considerably, as the
structures of interest may not clear the SNR threshold for the mask.

Note that alternatives to the zero-masking approach do exist for other
iterative map-makers. For example, \citet{kovacs2008} typically
restricts the solution to a small fixed number of iterations (of order
$\sim$10), although we note that there is no guarantee that maps will
have reasonably converged with such a strategy. For BOLOCAM data of
the Galactic Plane, \citet{aguirre2010} used a Maximum-Entropy
filtering step to suppress large-scales. As in the case of the
SNR-based masking described here, Maximum-Entropy filtering is also
non-linear, meaning that it too requires simulations to establish its
transfer function and noise properties as a function of angular scale.

@@

\item SMURF is an iterative map-maker that can produce SCUBA-2 maps on
single high-end modern desktops in a reasonable amount of time.

\item A simple model which removes most noise in a common-mode
rejection step, along with high-pass filtering, results in maps that
approach the white-noise performance of the detectors.

\item The main problem to overcome with our strategy is the divergence
of the map on large angular scales, due to the degeneracy between the
map, common-mode, and other residual low-frequency noise. A simple
strategy of constraining empty regions of the map to zero (either a
user-supplied mask for known sources, or an iterative determination of
signal above some SNR threshold) provides good constraints for compact
objects, and bright/extended structures.

\item For maps of faint point sources, a single (non-iterative)
high-pass filter at the start of the reduction produces maps that are
nearly white-noise limited. We illustatre how to completely whiten the
maps using jackknife measurements of the angular noise power spectrum
in order to reliably extract sources down to the limits of the map.

\item The map-maker has an automatic stopping criterion based on the
change in the map and $\chi^2$ between subsequent iterations, allowing
it to adapt to a wide range of data in a pipeline setting.

\item It is believed that a maximum-likelihood map-maker, such as
SANEPIC, will provide improved maps over the iterative algorithm
described here. However, SMURF will most likely be used as an initial
step in such processing since it can quickly clean the bolometer
time-series, as well as perform map-based despiking (a necessarily
iterative step).

%\scuba\ is being re-commissioned. Maybe we will have some initial data
%on fridge performance? If both it, and sky noise are relatively
%well-behaved, might be able to restrict filtering to lower frequencies
%and get larger-scale structures.

%Larger array footprint also helps.

%Talk about potential of Pascale et al. method to get closer to
%max-likelihood map solution (handle maps at constant scan angles with
%weights in Fourier space separately).
